What is an Ancestral Recombination Graph?

### 2022-02-13 paper.tex

We describe here an alternative formulation in which the
concepts are based on the diploid pedigree, which
is free from the limitations discussed in the previous section.
\cite{mathieson2020ancestry} and others
\citep{wakeley2012genetics,gusfield2014recombinatorics,speed2015naturereviewsgenetics}
have also suggested this approach, although without explicitly defining
the roles of nodes and the details of how ancestry
flows along edges.
\begin{figure}
\vspace{5em}
\caption{\label{fig-pedigree-and-arg}
The (unannotated) ARG is closely related to the pedigree
graph, where each ``individual'' node is replace by two ``genome''
nodes, and edges between parents and children are only included if there is
transfer of ancestral material. We usually only include nodes in an ARG
that affect our sample, so that, for example, individuals that are ancestral
to only one sampled genome are not included.}
\end{figure}

>>>>

We describe here an alternative formulation in which the
concepts are based on the diploid pedigree, which
is free from the limitations discussed in the previous section.
\citet{mathieson2020ancestry} and others
\citep{wakeley2012genetics,gusfield2014recombinatorics,speed2015naturereviewsgenetics}
have also suggested this approach, although without explicitly defining
the roles of nodes and the details of how ancestry
flows along edges.
\begin{figure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.3\textheight]{illustrations/pedigree}
    \caption{Pedigree with genetic inheritance}
    \label{fig:pedigree}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.3\textheight]{illustrations/pedigree_ARG}
    \caption{Graph representation of genetic inheritance}
    \label{fig:ARG-of-pedigree}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.3\textheight]{illustrations/pedigree_trees}
    \caption{Tree representation of genetic inheritance}
    \label{fig:ts-of-pedigree}
  \end{subfigure}
\caption{\label{fig-pedigree-and-arg}
The (unannotated) ARG is closely related to the pedigree
graph, where each ``individual'' node is replaced by two ``genome''
nodes, and edges between parents and children are only included if there is
transfer of ancestral material. We usually only include nodes in an ARG
that affect our sample, so that, for example, individuals that are ancestral
to only one sampled genome are not included.}
\end{figure}
